Clean spectral data

### 2020-09-15 R/clean_spectral_data.Rmd
running through the clean data script again
looks like there is more data than before - I wonder if that's because there is newer data from this past season

```{r}
# read_csv --> no factors, creates a tibble
all_spectra <- read_csv(here::here("analysis","data","raw_data",
                                   "spectral-lib","all_spectra.csv"))
```

>>>>

```{r}
# read_csv --> no factors, creates a tibble
all_spectra <- read_csv(here::here("analysis","data","raw_data",
                                   "spectral-lib","all_spectra.csv"))

# quick look at the values in each column
glimpse(all_spectra)
```
